Effects of Reynolds Number on the Performance and Near-Wake of a Cross-Flow Turbine

### 2014-06-16 paper.tex
Add description of wake measurement locations

A wake map was generated by positioning a Nortek Vectrino+ acoustic Doppler Velocimeter (ADV) at

@@

\authorcontributions{Author Contributions}

\todo[inline]{Is this section necessary?}

>>>>

A wake map was generated by positioning a Nortek Vectrino+ acoustic Doppler
Velocimeter (ADV) at 270 different locations, varied in the cross-stream and
vertical directions at one turbine diameter downstream. These locations have
vertical coordinates from the turbine centerline up to $z/H=0.625$, ranging in
the cross-stream direction $y/R = \pm 3$. These locations are show in
Figure~\ref{fig:wake_locations}.

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{figures/wake_meas_grid}
\caption{Wake measurement coordinate system and locations.}
\label{fig:wake_locations}
\end{figure}

@@
